---
title: "c3dr"
format: gfm
knitr:
  opts_chunk: 
    collapse: true
    comment: "#>" 
---

<!-- README.md is generated from README.qmd. Please edit that file -->

<!-- badges: start -->

[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Status at rOpenSci Software Peer Review](https://badges.ropensci.org/686_status.svg)](https://github.com/ropensci/software-review/issues/686)
[![CRAN status](https://www.r-pkg.org/badges/version/c3dr)](https://CRAN.R-project.org/package=c3dr)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.14870399.svg)](https://doi.org/10.5281/zenodo.14870399)
[![R-CMD-check](https://github.com/ropensci/c3dr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ropensci/c3dr/actions/workflows/R-CMD-check.yaml)
[![codecov](https://codecov.io/gh/ropensci/c3dr/graph/badge.svg?token=7lAu5XzivG)](https://app.codecov.io/gh/ropensci/c3dr)
<!-- badges: end -->

## Overview

An R package for working with motion capture data based on the C++ library [EZC3D](https://github.com/pyomeca/ezc3d).

## Background

C3D (<https://www.c3d.org/>) is a file format for biomechanical data, namely motion capture recordings with additional analog data (e.g., from force plates or electromyography).

The `c3dr` package allows to read, analyze and write C3D files in R (<https://www.r-project.org/about.html>), a programming language popular for statistical analyses and data visualization. `c3dr` is build on the open-source C++ library EZC3D (<https://github.com/pyomeca/ezc3d>).

For more information, read the [Get Started](https://docs.ropensci.org/c3dr/articles/c3dr.html) vignette.

## Installation

Install the `c3dr` package from CRAN:

```{r}
#| eval: false
install.packages("c3dr")
```

Alternatively, you can the latest development version from R-Universe:

```{r}
#| eval: false
install.packages("c3dr", repos = "https://ropensci.r-universe.dev")
```

## Usage

### Read Data

```{r}
library(c3dr)

# get example data. Insert your file path instead, e.g.
# path <- "folder/myfilename.c3d"
path <- c3d_example()

# import data
d <- c3d_read(path)
d

# structure of the imported object
str(d, max.level = 1)

# read point data
p <- c3d_data(d)
p[1:5, 1:5]

# alternative long data format
p_long <- c3d_data(d, format = "long")
p_long[1:5, 1:5]

# read analog data
a <- c3d_analog(d)
a[1:5, 41:43]

# read data from first force platform
d$forceplatform[[1]]$forces[1:5, ]

# write data to a new c3d file
# c3d_write(d, "newfile.c3d")
```

## Citation

```{r}
#| comment: ""
#| collapse: false
citation("c3dr")
```

## Acknowledgements

The following people have contributed to this package by providing raw data files, testing code, suggesting features and/or reviewing the package: Björn Braunstein, July Pilowsky, Theresa Siepe, Aymeric Stamm.

## Contributing

If you consider contributing to this package, read the [CONTRIBUTING.md](https://github.com/ropensci/c3dr/blob/main/.github/CONTRIBUTING.md). 
Please note that this package is released with a [Contributor Code of Conduct](https://ropensci.org/code-of-conduct/). 
By contributing to this project, you agree to abide by its terms.

## Funding

This project was funded by the Internal Research Funds of the [German Sport University Cologne](https://www.dshs-koeln.de/english/), grant agreement number L-11-10011-289-154000.
