---
title: "c3dr"
format: gfm
---

<!-- README.md is generated from README.qmd. Please edit that file -->

<!-- badges: start -->

[![Project Status: WIP – Initial development is in progress, but there has not yet been a stable, usable release suitable for the public.](https://www.repostatus.org/badges/latest/wip.svg)](https://www.repostatus.org/#wip) [![R-CMD-check](https://github.com/smnnlt/c3dr/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/smnnlt/c3dr/actions/workflows/R-CMD-check.yaml) [![codecov](https://codecov.io/gh/smnnlt/c3dr/graph/badge.svg?token=BTRQJ0A831)](https://codecov.io/gh/smnnlt/c3dr)

<!-- badges: end -->

## Overview

An R package for working with motion capture data based on the C++ library [EZC3D](https://github.com/pyomeca/ezc3d).

## Background

## Installation

Install `c3dr` from GitHub:

```{r}
#| eval: false
if (!require(pak)) install.packages("pak")
pak::pak("smnnlt/c3dr")
```

## Usage

### Import Data

```{r}
#| collapse: true
#| comment: "#>"
library(c3dr)

# get example data. Insert your file path instead
path <- c3d_example() 

# import data
d <- c3d_read(path)
d

# structure of the imported object
str(d, max.level = 1)

# read point data
p <- c3d_data(d)
p[1:5, 1:5]

# alternative long data format
p_long <- c3d_data(d, format = "long")
p_long[1:5, 1:5]

# read analog data
a <- c3d_analog(d)
head(a)
```

## Citation

## Contributing

If you consider contributing to this package, read the [CONTRIBUTING.md](https://github.com/smnnlt/c3dr/blob/main/.github/CONTRIBUTING.md). Please note that the c3dr project is released with a [Contributor Code of Conduct](https://github.com/smnnlt/c3dr/blob/main/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

## Funding

This project was funded by the Internal Research Funds of the [German Sport University Cologne](https://www.dshs-koeln.de/english/), grant agreement number L-11-10011-289-154000.
